---
title: "clustering"
author: "Amanda Freitas"
date: "2023-05-17"
output: html_document
---

```{r}
library(igraph)
```

# BABARASI-ALBERT GRAPHS

## GENERATING GRAPHS  
  
- Mesmo modelo e mesmos parâmetros


```{r}
set.seed(1998)
barabasi_graph01 <- barabasi.game(
  n = 100,
  power = 0.4,
  m = 2,
  directed = F
)

barabasi_graph02 <- barabasi.game(
  n = 100,
  power = 0.4,
  m = 2,
  directed = F
)

barabasi_graph03 <- barabasi.game(
  n = 100,
  power = 0.4,
  m = 2,
  directed = F
)
```


- Mesmo modelo e parâmetros distintos
```{r}
set.seed(1999)

barabasi_graph04 <- barabasi.game(
  n = 200,
  power = 0.6,
  m = 2,
  directed = F
)

barabasi_graph05 <- barabasi.game(
  n = 200,
  power = 0.6,
  m = 2,
  directed = F
)

barabasi_graph06 <- barabasi.game(
  n = 220,
  power = 0.3,
  m = 2,
  directed = F
)
```


## SAVING IGRAPH_OBJECTS

```{r}
write_graph(barabasi_graph01,
            file = "barabasi_graphs/objects/barabasi_graph01.txt",
            format = "edgelist")
```


```{r}
write_graph(barabasi_graph02,
            file = "barabasi_graphs/objects/barabasi_graph02.txt",
            format = "edgelist")
```

```{r}
write_graph(barabasi_graph03,
            file = "barabasi_graphs/objects/barabasi_graph03.txt",
            format = "edgelist")
```


```{r}
write_graph(barabasi_graph04,
            file = "barabasi_graphs/objects/barabasi_graph04.txt",
            format = "edgelist")
```


```{r}
write_graph(barabasi_graph05,
            file = "barabasi_graphs/objects/barabasi_graph05.txt",
            format = "edgelist")
```


```{r}
write_graph(barabasi_graph06,
            file = "barabasi_graphs/objects/barabasi_graph06.txt",
            format = "edgelist")
```



## PLOTTING AND SAVING PLOTS

```{r}
tiff("barabasi_graphs/plots/barabasi_graph01.png", units="in", width=5, height=5, res=300)

plot(barabasi_graph01,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("barabasi_graphs/plots/barabasi_graph02.png", units="in", width=5, height=5, res=300)

plot(barabasi_graph02,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("barabasi_graphs/plots/barabasi_graph03.png", units="in", width=5, height=5, res=300)

plot(barabasi_graph03,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("barabasi_graphs/plots/barabasi_graph04.png", units="in", width=5, height=5, res=300)

plot(barabasi_graph04,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```


```{r}
tiff("barabasi_graphs/plots/barabasi_graph05.png", units="in", width=5, height=5, res=300)

plot(barabasi_graph05,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("barabasi_graphs/plots/barabasi_graph06.png", units="in", width=5, height=5, res=300)

plot(barabasi_graph06,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```


#ERDOS_RENYI GRAPHS

## GENERATING GRAPHS
- Mesmo modelo e mesmos parâmetros
```{r}
set.seed(1998)

erdos_renyi_graph01 <- erdos.renyi.game(
  n = 50,
  p = 0.3,
  directed = F,
  loops = F
)


erdos_renyi_graph02 <- erdos.renyi.game(
  n = 50,
  p = 0.3,
  directed = F,
  loops = F
)

erdos_renyi_graph03 <- erdos.renyi.game(
  n = 50,
  p = 0.3,
  directed = F,
  loops = F
)
```

- Mesmo modelo e parâmetros distintos
```{r}
set.seed(1999)
erdos_renyi_graph04 <- erdos.renyi.game(
  n = 50,
  p = 0.15,
  directed = F,
  loops = F
)

erdos_renyi_graph05 <- erdos.renyi.game(
  n = 50,
  p = 0.15,
  directed = F,
  loops = F
)

erdos_renyi_graph06 <- erdos.renyi.game(
  n = 55,
  p = 0.2,
  directed = F,
  loops = F
)

```




## SAVING IGRAPH_OBJECTS

```{r}
write_graph(erdos_renyi_graph01,
            file = "erdos_renyi_graphs/objects/erdos_renyi_graph01.txt",
            format = "edgelist")

write_graph(erdos_renyi_graph02,
            file = "erdos_renyi_graphs/objects/erdos_renyi_graph02.txt",
            format = "edgelist")

write_graph(erdos_renyi_graph03,
            file = "erdos_renyi_graphs/objects/erdos_renyi_graph03.txt",
            format = "edgelist")

write_graph(erdos_renyi_graph04,
            file = "erdos_renyi_graphs/objects/erdos_renyi_graph04.txt",
            format = "edgelist")

write_graph(erdos_renyi_graph05,
            file = "erdos_renyi_graphs/objects/erdos_renyi_graph05.txt",
            format = "edgelist")


write_graph(erdos_renyi_graph06,
            file = "erdos_renyi_graphs/objects/erdos_renyi_graph06.txt",
            format = "edgelist")


```


## PLOTTING AND SAVING PLOTS

```{r}
tiff("erdos_renyi_graphs/plots/erdos_renyi_graph01.png", units="in", width=5, height=5, res=300)

plot(erdos_renyi_graph01,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("erdos_renyi_graphs/plots/erdos_renyi_graph02.png", units="in", width=5, height=5, res=300)

plot(erdos_renyi_graph02,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("erdos_renyi_graphs/plots/erdos_renyi_graph03.png", units="in", width=5, height=5, res=300)

plot(erdos_renyi_graph03,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("erdos_renyi_graphs/plots/erdos_renyi_graph04.png", units="in", width=5, height=5, res=300)

plot(erdos_renyi_graph04,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("erdos_renyi_graphs/plots/erdos_renyi_graph05.png", units="in", width=5, height=5, res=300)

plot(erdos_renyi_graph05,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("erdos_renyi_graphs/plots/erdos_renyi_graph06.png", units="in", width=5, height=5, res=300)

plot(erdos_renyi_graph06,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```


# WATTS-STROGATZ GRAPHS

## GENERATING GRAPHS  

- Mesmo modelo e mesmos parâmetros
```{r}
set.seed(1998)

watts_graph01 <- sample_smallworld(dim = 1,
                  size = 100,
                  nei = 5,
                  p = 0.05,
                  loops = F)

watts_graph02 <- sample_smallworld(dim = 1,
                  size = 100,
                  nei = 5,
                  p = 0.05,
                  loops = F)

watts_graph03 <- sample_smallworld(dim = 1,
                  size = 100,
                  nei = 5,
                  p = 0.05,
                  loops = F)
```


- Mesmo modelo e parâmetros distintos
```{r}
set.seed(1999)

watts_graph04 <- sample_smallworld(dim = 1,
                  size = 50,
                  nei = 6,
                  p = 0.07,
                  loops = F)

watts_graph05 <- sample_smallworld(dim = 1,
                  size = 50,
                  nei = 6,
                  p = 0.07,
                  loops = F)

watts_graph06 <- sample_smallworld(dim = 1,
                  size = 60,
                  nei = 3,
                  p = 0.04,
                  loops = F)
```


```{r}
summary(watts_graph01)
```


## SAVING IGRAPH_OBJECTS

```{r}
write_graph(watts_graph01,
            file = "watts_strogatz_graphs/objects/watts_graph01.txt",
            format = "edgelist")

write_graph(watts_graph02,
            file = "watts_strogatz_graphs/objects/watts_graph02.txt",
            format = "edgelist")

write_graph(watts_graph03,
            file = "watts_strogatz_graphs/objects/watts_graph03.txt",
            format = "edgelist")


write_graph(watts_graph04,
            file = "watts_strogatz_graphs/objects/watts_graph04.txt",
            format = "edgelist")

write_graph(watts_graph05,
            file = "watts_strogatz_graphs/objects/watts_graph05.txt",
            format = "edgelist")

write_graph(watts_graph06,
            file = "watts_strogatz_graphs/objects/watts_graph06.txt",
            format = "edgelist")
```

## PLOTTING AND SAVING PLOTS

```{r}
tiff("watts_strogatz_graphs/plots/watts_graph01.png", units="in", width=5, height=5, res=300)

plot(watts_graph01,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("watts_strogatz_graphs/plots/watts_graph02.png", units="in", width=5, height=5, res=300)

plot(watts_graph02,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("watts_strogatz_graphs/plots/watts_graph03.png", units="in", width=5, height=5, res=300)

plot(watts_graph03,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("watts_strogatz_graphs/plots/watts_graph04.png", units="in", width=5, height=5, res=300)

plot(watts_graph04,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("watts_strogatz_graphs/plots/watts_graph05.png", units="in", width=5, height=5, res=300)

plot(watts_graph05,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```

```{r}
tiff("watts_strogatz_graphs/plots/watts_graph06.png", units="in", width=5, height=5, res=300)

plot(watts_graph06,
     layout=layout_with_fr, 
     vertex.size=4,
     vertex.color="black", 
     edge.arrow.size=0.4,
     vertex.label = NA)

dev.off()
```